\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Jon\'a\v{s} Proch\'azka} \\ \vspace{1pt}
    Pilsen, Czech Republic \\ \vspace{1pt}
    \small \href{mailto:jonasprochaz@gmail.com}{\underline{jonasprochaz@gmail.com}} $|$ 
    +420 777 079 627 $|$
    \href{https://github.com/jonasproch}{\underline{github.com/jonasproch}}
\end{center}

\section{Profile}
\small
Third year Cybernetics student at the University of West Bohemia with a focus on automation, robotics, control, and software systems. Currently working on a bachelor's thesis on uncertainty propagation of objects in orbit and employed part time as a software developer. Interested in scientific computing, robotics, applied mathematics, and technically demanding software engineering roles in research oriented environments.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of West Bohemia, Faculty of Applied Sciences}{Pilsen, Czech Republic}
      {BSc in Cybernetics and Robotics}{Sep 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Relevant areas: automation, control engineering, robotics, embedded systems, programming, and applied mathematics.}
        \resumeItem{Bachelor's thesis: \textit{Representation of uncertainty in the position and velocity of an object in orbit}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Apollo Data s.r.o.}{Pilsen, Czech Republic}
      {Software Developer}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Build client applications using \textbf{.NET, MS SQL, TypeScript, and React} across backend, database, and frontend layers.}
        \resumeItem{Deliver features end to end, including business logic, database integration, and user interface implementation.}
        \resumeItem{Contribute to production software with emphasis on reliability, maintainability, and practical usability.}
        \resumeItem{Work within a professional software development workflow using Git and iterative delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {SentiSquare s.r.o.}{Pilsen, Czech Republic}
      {Web Developer}{Feb 2023 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Developed web application frontend features using \textbf{React and TypeScript}.}
        \resumeItem{Built and maintained reusable user interface components in a team development environment.}
        \resumeItem{Contributed to modern frontend development practices and maintainable codebases.}
      \resumeItemListEnd

    \resumeSubheading
      {TerritorioVirtual}{M\'alaga, Spain}
      {Web Development Intern}{Jul 2022 -- Jul 2022}
      \resumeItemListStart
        \resumeItem{Completed an \textbf{Erasmus internship} focused on web development.}
        \resumeItem{Contributed to a sports club management platform in an international work environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Bachelor's Thesis: Uncertainty Propagation of Objects in Orbit} $|$ \emph{Research project}}{Sep 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Compare approaches for propagating uncertainty in orbital position and velocity across different coordinate systems.}
            \resumeItem{Apply mathematical modeling and numerical analysis to orbital dynamics.}
            \resumeItem{Investigate representation and interpretation of uncertainty in dynamical systems.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{St\"aubli TX40 Robot Kinematics and Control Project} $|$ \emph{MATLAB, Simulink, Simscape, Rexygen}}{Oct 2025 -- Jan 2026}
          \resumeItemListStart
            \resumeItem{Developed forward and inverse kinematics, Jacobian calculations, and trajectory planning for a 6 axis industrial robot.}
            \resumeItem{Built and validated simulation models in MATLAB, Simulink, and Simscape.}
            \resumeItem{Integrated Rexygen based control and visualization components for motion analysis and robot behavior verification.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Autonomous Line Following and Maze Solving Robot} $|$ \emph{Embedded robotics project}}{Mar 2025 -- Jul 2025}
          \resumeItemListStart
            \resumeItem{Programmed an autonomous wheeled robot for line following, maze solving, and shortest path execution.}
            \resumeItem{Implemented navigation logic and control behavior for repeated runs and path optimization.}
            \resumeItem{Applied embedded and robotics principles in a practical hardware software system.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C++, C\#, TypeScript, MATLAB, SQL} \\
     \textbf{Frameworks \& Tools}{: React, .NET, Git, Linux, Simulink, Simscape, Rexygen} \\
     \textbf{Domains}{: Robotics, Control Engineering, Embedded Systems, Mathematical Modeling, Scientific Computing}
    }}
 \end{itemize}

\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Czech}{: Native} \\
     \textbf{English}{: C1}
    }}
 \end{itemize}

\section{Interests}
\small Space technology, motorsport, running, hiking

\end{document}
